### 2017-07-15 KineticModel/estimation/docs/formulation/noisy_estimate.tex
clearly specify index dimensions
updates to formulation for estimation

	\paragraph{Suggested modifications to address infeasibility (July 4)}
	After discussion with Prof. M, the following changes were made to the problem formulation:
	\begin{itemize}
		\item Experimental fluxes may/may not be at steady state. Accordingly, using the steady state constraint in the above formulation can render the optimization problem infeasible. Suggestion is to remove this constraint(s).
		\item Include the norm minimization constraint as an objective.
		\item Add the noise in fluxes and concentrations as part of the bound constraint.
		\begin{center}
			\begin{subequations}
				\begin{align}
				\underset{x,p_i}{\mathrm{min}} & \text{      }\left\Vert v_i-v^*\right\Vert\\
				& \text{      }v_i = f(x,p_i)\\
				& \text{      }x_{min}(1-\epsilon)\le x \le x_{max}(1+\epsilon)\\
				%& \text{      }v_{min}(1-\epsilon)\le v \le v_{max}(1+\epsilon)\\
				& \text{      }p_{i,min} \le p_i \le p_{i,max}\\
				\end{align}
			\end{subequations}
		\end{center}
	\item The noise $\epsilon$ is fixed at 5\% or 10\% to signify experimental noise.
	\end{itemize}

>>>>

	\paragraph{Suggested modifications to address infeasibility (July 4)}
	After discussion with Prof. M, the following changes were made to the problem formulation:
	\begin{itemize}
		\item Experimental fluxes may/may not be at steady state. Accordingly, using the steady state constraint in the above formulation can render the optimization problem infeasible. Suggestion is to remove this constraint(s).
		\item Include the norm minimization constraint as an objective.
		\item Add the noise in fluxes and concentrations as part of the bound constraint.
		\begin{center}
			\begin{subequations}
				\begin{align}
				\underset{x,p_j}{\mathrm{min}} & \text{      }\left\Vert v_i-v^*\right\Vert &  i\in\mathcal{R}^n,\text{  }j\in\mathcal{R}^l\\
				\mathrm{st}& \text{      }v_i = f(x,p_j)\\
				& \text{      }x_{min}(1-\epsilon)\le x \le x_{max}(1+\epsilon)\\
				%& \text{      }v_{min}(1-\epsilon)\le v \le v_{max}(1+\epsilon)\\
				& \text{      }p_{j,min} \le p_j \le p_{j,max}
				\end{align}
			\end{subequations}
		\end{center}
	\item The noise $\epsilon$ is fixed at 5\% or 10\% to signify experimental noise.
	\end{itemize}

	\paragraph{More changes to address nonlinearity due to division(July 13)}
	Prof. M suggested changing the nonlinear formulation of the flux equations into just a bilinear form by removing the denominator and formulating it as nonlinear algebraic equation.
	\begin{center}
		\begin{subequations}
			\begin{align}
			\underset{x,p_j,v_i}{\mathrm{min}} & \text{      }\left\Vert v_i-v^*\right\Vert &  i\in\mathcal{R}^n,\text{  }j\in\mathcal{R}^l\\
			\mathrm{st}& \text{      }N(x,p_j) - v_iD(x,p_j) = 0\\
			& \text{      }x_{min}(1-\epsilon)\le x \le x_{max}(1+\epsilon)\\			
			& \text{      }p_{j,min} \le p_j \le p_{j,max}\\
			& \text{      }v_{i,min}(1-\epsilon)\le v_i \le v_{i,max}(1+\epsilon)
			\end{align}
		\end{subequations}
	\end{center}

	\begin{itemize}
		\item Also, the initial noise added to the steady state solutions was reduced from 50\% to 5\% or 10\%.
		\item $\epsilon$ is fixed at 50\%.
		\item Solution is obtained using multisolve with IPOPT instead of aiming to obtain a global solution with SCIP.
		\item Using approximately 14 million points for the second phase of multistart in OPTI
	\end{itemize}
